---
title: "homework-number-5"
author: "Ingrid Lundeen and Rachel Voyt"
date: "November 16, 2016"
output: html_document
---
#Ingrid L and Rachel V
```{r}
library(curl) #attach the appropriate package
f <- curl("https://raw.githubusercontent.com/difiore/ADA2016/master/KamilarAndCooperData.csv") #use curl function to pull in the link for the data
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = TRUE) #read in the csv as data
```
##Run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your beta coefficients (slope and intercept)
```{r}
a<-lm(log(HomeRange_km2)~log(Body_mass_female_mean), data=d) 
summary(a)
confint(a, level=0.95)
a$coefficients

```
##Use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each beta coefficient
```{r}
bboot <- numeric(1000)
for(i in 1:1000) {
   this.ind <- sample(213, 213, replace=TRUE)
   bboot[i] <- coef(lm(
      log(d$HomeRange_km2)[this.ind]~log(d$Body_mass_female_mean)[this.ind]))[1]
}

boot<-numeric(1000)
for(i in 1:1000) {
   this.ind <- sample(213, 213, replace=TRUE)
   boot[i] <- coef(lm(
      log(d$HomeRange_km2)[this.ind]~log(d$Body_mass_female_mean)[this.ind]))[2]
}

bootsee<-bootCase(a, f.=coef, B=1000)
bootsee
mean(bootsee[,1])
se(bootsee[,1])
quantile(bootsee [,1], c(0.025, 0.975))
```
##Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution
```{r}
library(sciplot)
se(bboot)
hist(bboot)
mean(bboot)
bbootci <- quantile(bboot, c(0.025, 0.975))
bbootci

se(boot)
hist(boot)
mean(boot)
bootci <- quantile(boot, c(0.025, 0.975))
bootci
```
## How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?
### The standard error estimated from the entire data set is much higher than the standard errors from our bootstrapped sampling distributions. 

## How does the latter compare to the 95% CI estimated from your entire dataset?
### The confidence intervals calculated for our (b)bootci estimates are slightly wider that for our entire dataset

##Extra Credit +2
```{r}
#THIS ONE DOESN'T WORK YET
bootsy<-function(d, m, conf.level=0.95, n=1000){
  model<-lm(m, data=d)
  intercept<-coefficients(model)[1]
  slope<-coefficients(model)[2]
  intercept_standard_error<-summary(model)$coefficients[1,2]
  slope_standard_error<-summary(model)$coefficients[2,2]
  confidence_interval<-confint(model, level=conf.level)
  numb<-length(d[ ,1])
  boot_int<-numeric(n)
  for(i in 1:n) {
   this.ind <- sample(numb, numb, replace=TRUE)
   boot_int[i] <- coef(lm(m))[1]
  }
  bootstrap_interval_mean<-mean(boot_int)
  bootstrap_interval_standardError<-se(boot_int)
  bootstrap_interval_conf.int<- quantile(boot_int, c(0.025, 0.975))
  boot_slope<-numeric(n)
  for(i in 1:n) {
    this.ind1<-sample(numb,numb,replace=TRUE)
    boot_slope[i]<-coef(lm(m))[2]
  }
  bootstrap_slope_mean<-mean(boot_int)
  bootstrap_slope_standardError<-se(boot_int)
  bootstrap_slope_conf.int<- quantile(boot_int, c(0.025, 0.975))
  return(c(intercept,slope, intercept_standard_error, slope_standard_error, confidence_interval, bootstrap_interval_mean, bootstrap_interval_standardError, bootstrap_interval_conf.int, bootstrap_slope_mean, bootstrap_slope_standardError, bootstrap_slope_conf.int))
}

```


```{r}
#THIS ONE DOESNT REALLY WORK
bootsy<-function(d, m, conf.level=0.95, n=1000){
  model<-lm(m, data=d)
  intercept<-coefficients(model)[1]
  slope<-coefficients(model)[2]
  intercept_standard_error<-summary(model)$coefficients[1,2]
  slope_standard_error<-summary(model)$coefficients[2,2]
  confidence_interval<-confint(model, level=conf.level)
  bootsie<-bootCase(model, f.=coef, B=1000)
  bootstrap_interval_mean<-mean(bootsie[,1])
  bootstrap_interval_standardError<-se(bootsie[,1])
  bootstrap_interval_conf.int<- quantile(bootsie [,1], c(0.025, 0.975))
  bootstrap_slope_mean<-mean(bootsie[,2])
  bootstrap_slope_standardError<-se(bootsie[,2])
  bootstrap_slope_conf.int<- quantile(boot_int[,2], c(0.025, 0.975))
  return(c(intercept,slope, intercept_standard_error, slope_standard_error, confidence_interval, bootstrap_interval_mean, bootstrap_interval_standardError, bootstrap_interval_conf.int, bootstrap_slope_mean, bootstrap_slope_standardError, bootstrap_slope_conf.int))
}

p<-bootsy(d, a, conf.level=0.95, n=1000)
p
```
